Election Violence Newspaper Article Selection Process Pilot: Evaluate Keyword Selection Method

### 2018-08-13 other_R_code/article_selection_pilot_evaluate_NBkeywordmethods.Rnw
minor changes to text

\documentclass{article}
\usepackage[margin=1in]{geometry}
\title{Election Violence Newspaper Article Selection Process Pilot: Evaluate Keyword Selection Method}
\begin{document}
\maketitle
\section{Summary}
After the code to setup and download data (Sections \ref{sect:packages}-\ref{sect:download1832}) the document below includes:
First, an implementation of code to select of articles for coding, where initial evaluation of articles is based on keywords from the boolean searches which return those articles (Sections \ref{sect:whichdownloadocr}-\ref{sect:useonocr}). This classification is done using actual searches conducted (effectively 4 keywords) with a Naive Bayes classifier.

Second, the document then provides an evaluation of the keyword selection step based on user classified articles from the platform with Naive Bayes and other classifiers and with 4 and 10 keyword sets (Sections \ref{sect:eval4nb}-\ref{sect:eval10other}).

Finally, to provide an alternative way of evaluating the process, the document includes 10 randomly selected cases which are rejected for coding in the implementation code (Section \ref{sect:rejectnbprocess}).

\section{Packages used}
\label{sect:packages}
<<setuppath, echo=FALSE, results="hide">>=
dropbox.path<-switch (Sys.info()["nodename"],
                      "DM-GIA-051"="D:/Dropbox",
                      "DM-GIA-055"="D:/Dropbox",
                      "GIDON-ASUS-15"="C:/Users/Gidon/Dropbox",
                      "GID-HOME-LENOVO"="C:/Users/Gidon/Dropbox")

@@

<<pilot.packages, warning=FALSE, message=FALSE>>=

>>>>

\documentclass{article}
\usepackage[margin=1in]{geometry}
\title{Election Violence Newspaper Article Selection Process Pilot: Evaluate Keyword Selection Method}
\begin{document}
\maketitle
\section{Summary}
The document below includes:
Evaluates of the selection of articles using keywords with Naive Bayes with 4, 10 and all keyword sets.

\label{sect:packages}
<<setuppath, echo=FALSE, results="hide">>=
dropbox.path<-switch (Sys.info()["nodename"],
                      "DM-GIA-051"="D:/Dropbox",
                      "DM-GIA-055"="D:/Dropbox",
                      "GIDON-ASUS-15"="C:/Users/Gidon/Dropbox",
                      "GID-HOME-LENOVO"="C:/Users/Gidon/Dropbox")

@@

<<pilot.packages, echo=FALSE, warning=FALSE, message=FALSE>>=
